\vspace{1.0cm} \LARGE \bf Reassortment between influenza B lineages and the emergence of a co-adapted PB1-PB2-HA gene complex

### 2014-02-06 fluB.tex
Add language to distinguish lineages that associate from lineages that derive. Per #7.

\begin{figure}[h]
	\centering	
	\includegraphics[width=0.65\textwidth]	{figures/InfB_LineageRatiosOverTime.png}
	\caption{\textbf{Ratio of lineages in the dataset.}
The ratio of Victoria (red) to Yamagata (blue) lineage sequences in each segment over time.
Yamagata lineage PA, NP, NA and MP segments and Victoria lineage NS segment eventually become fixed in the influenza B population.
PB1, PB2 and HA segments maintain separate Victoria and Yamagata lineages.}
	\label{lineageRatiosOverTime}
\end{figure}

@@

\begin{figure}[h]
	\centering		
	\includegraphics[width=0.95\textwidth]{figures/RailroadPlotDated.pdf}
	\caption{\textbf{Schematic plot of reconstructed reassortments between Victoria and Yamagata lineage segments of influenza B virus.}
Victoria and Yamagata lineage genomes are represented by 8 (red or blue, respectively) parallel lines.
Inter-lineage reassortment events are indicated by lines entering a different genome.
The angle of incoming lineages represents uncertainty in the timing of the event (mean date of the reassortant node and its parent node).
Lineage extinction dates are not shown accurately.
\tbc{Giving this a bit more vertical spread (increasing aspect ratio) would likely clarify things a bit.}}
	\label{railroadPlot}
\end{figure}

>>>>

\begin{figure}[h]
	\centering	
	\includegraphics[width=0.65\textwidth]	{figures/InfB_LineageRatiosOverTime.png}
	\caption{\textbf{Ratio of lineages in the dataset.}
The ratio of sequences that derive from the original Victoria clade (red) to sequences that drive from the Yamagata clade (blue) lineage sequences in each segment over time.
Yamagata lineage PA, NP, NA and MP segments and Victoria lineage NS segment eventually become fixed in the influenza B population.
PB1, PB2 and HA segments maintain separate Victoria and Yamagata lineages.}
	\label{lineageRatiosOverTime}
\end{figure}

@@

\begin{figure}[h]
	\centering		
	\includegraphics[width=0.95\textwidth]{figures/RailroadPlotDated.pdf}
	\caption{\textbf{Schematic plot of reconstructed reassortments between Victoria and Yamagata lineage segments of influenza B virus.}
Lineages that coassort in genomes are represented by 8 parallel lines, with lineages that derive from the original Victoria clade colored red and lineages that derive from the original Yamagata clade colored blue.
Inter-lineage reassortment events are indicated by lines entering a different genome.
The angle of incoming lineages represents uncertainty in the timing of the event (mean date of the reassortant node and its parent node).
Lineage extinction dates are not shown accurately.
\tbc{Giving this a bit more vertical spread (increasing aspect ratio) would likely clarify things a bit.}}
	\label{railroadPlot}
\end{figure}
